---
title: "Collect all email addresses"
author: "Moritz Müller"
date: "6/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Load Libraries
NOTE: Data is in the RProject "sampling", just tranferred this here after running all below in the other project folder!
```{r}
library(stringr)
library(tidyverse)
library(dplyr)
```

# Read in all email addresses and combine them in one file
```{r}
#now extract addresses
folders.website <- data.frame(list.files("./data/scraped/extracted"), stringsAsFactors = F)

#initialize list for email collection
all_emails <- list()

for(i in 1:nrow(folders.website)){ 
  tryCatch({
    print(paste("Next Website:", folders.website[i,], "Number:", i))
    emails <- read.csv(file=paste0("./data/scraped/extracted/", folders.website[i,])) 
    emails <- emails %>% group_by(emails) %>% tally()
    emails$website <- str_extract(folders.website[i,], ".+?(?=-[0-9])")
    website_name <- str_extract(folders.website[i,], ".+?(?=-[0-9])")
    if(nrow(emails)>0){
      all_emails[[website_name]] <- as.data.frame(emails)}
  }, error = function(e){cat("ERROR: ", conditionMessage(e), "\n")})
  #, warning = function(e){cat("Warning: ", conditionMessage(e), "\n")})
}

#save(all_emails, file="data/all_emails")
load(file="data/all_emails")
```
# Create combindes dataframe with transparency database data and email of websites
```{r}
all_dfs = bind_rows(all_emails, .id = 'source')
all_dfs = all_dfs[!is.na(all_dfs$emails),]

##merge transparency dataset and scraped dataset
url_pattern <- "(?<=http[s]?://[www.]?)(?:[a-zA-Z]|[0-9]|[$-_@.&+]|[!*\\(\\),]|(?:%[0-9a-fA-F][0-9a-fA-F]))+"
smpl_rmng$website = str_extract(smpl_rmng$Website.address., url_pattern)
smpl_rmng$website=gsub("www.", "", smpl_rmng$website)

for (i in 1:nrow(smpl_rmng)){
  smpl_rmng$website[i]=strsplit(smpl_rmng$website[i], "/")[[c(1, 1)]]
}

### combine dfs from recommended.emails to dataframe, with website as column name
combined$website = gsub('.{7}$', '', combined$website)

mrg_data = inner_join(all_dfs, smpl_rmng, by="website")
```

# Match names
## Nitty gritty approach: All possible name combinations
```{r}
##match names and emails of PER organization
mrg_data$last = str_extract(mrg_data$Person.in.charge.of.EU.relations, '[^ ]+$')
mrg_data$first = word(mrg_data$Person.in.charge.of.EU.relations, 1)

# Other name combinations (courtesy of Saar Alon-Barkat's Github)
t1 <- str_split(mrg_data$last,"-", simplify = TRUE) %>% 
  data.frame() %>% 
  mutate(last.v1 = X1 %>% as.character(),
         last.v2 = X2 %>% as.character()) %>%
  select(-X1,
         -X2) %>% 
  mutate(last.v2 = na_if(last.v2,""))
mrg_data$last.v1 = t1$last.v1
mrg_data$last.v2 = t1$last.v2


mrg_data$first.v1 = str_split(mrg_data$first,"-", simplify = TRUE)

library(textclean)
mrg_data <- mrg_data %>% 
  #cleaning first and last names
  mutate(first.v1.clean = first.v1 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""),
         last.v1.clean = last.v1 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""),
         last.v2.clean = last.v2 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""))


##Creating acronyms of participant names:
t1 <- str_split(mrg_data$Person.in.charge.of.EU.relations," |-", simplify = TRUE) %>% 
  data.frame() %>% 
  mutate_all(funs(str_sub(.,1,1) %>%  str_to_lower())) %>% 
  mutate(person.name.acronym.v1 = str_c(X1,X2,X3,X4,X5)) %>% 
  mutate(person.name.acronym.v2 = str_c(str_sub(person.name.acronym.v1,1,1),
                                        str_sub(person.name.acronym.v1,-1,-1)))

t1 <- t1 %>% 
  mutate(person.name.acronym.v1 = t1$person.name.acronym.v1 %>% replace_non_ascii() %>% str_replace_all("\\W",""),
         person.name.acronym.v2 = t1$person.name.acronym.v2 %>% replace_non_ascii() %>% str_replace_all("\\W",""))
mrg_data$acronym.v1 = t1$person.name.acronym.v1
mrg_data$acronym.v2 = t1$person.name.acronym.v2

t1$person.name.acronym.v3 = paste0(t1$X1, ".", t1$X2, ".", t1$X3, ".", t1$X4)
t1$person.name.acronym.v3 = gsub("..", ".", t1$person.name.acronym.v3, fixed=T)
t1$person.name.acronym.v3 = t1$person.name.acronym.v3 %>% replace_non_ascii()
mrg_data$acronym.v3 =t1$person.name.acronym.v3

# Match
cmplt = mrg_data#[,c(1:3,57:63)]
cmplt$match = as.numeric(1)
cmplt = as.data.frame(cmplt)
library(stringi)
cmplt$emails_p = stri_extract_first_regex(cmplt$emails, "^[^@]+")

for (i in 1:nrow(cmplt)) {
  mrg_data$match[i] = sum(stri_detect_fixed(
    pattern = c(
      ifelse(is.na(tolower(mrg_data$last.v1.clean[i])), "jhgaskhdsg", tolower(mrg_data$last.v1.clean[i])),
      ifelse(is.na(tolower(mrg_data$last.v2.clean[i])), "jhgaskhdsg", tolower(mrg_data$last.v2.clean[i])),
      ifelse(is.na(tolower(mrg_data$first.v1.clean[i])), "jhgaskhdsg", tolower(mrg_data$first.v1.clean[i])),
      ifelse(is.na(tolower(mrg_data$first.v2.clean[i])), "jhgaskhdsg", tolower(mrg_data$first.v2.clean[i])),
      ifelse(is.na(tolower(mrg_data$acronym.v1[i])), "jhgaskhdsg", tolower(mrg_data$acronym.v1[i])),
      ifelse(is.na(tolower(mrg_data$acronym.v2[i])), "jhgaskhdsg", tolower(mrg_data$acronym.v2[i])),
      ifelse(is.na(tolower(mrg_data$acronym.v3[i])), "jhgaskhdsg", tolower(mrg_data$acronym.v3[i]))
    ),
    str = cmplt$emails_p[i]
  ))
}

test= mrg_data[mrg_data$match!=0,]
test= as.data.frame(test)
test =test[!is.na(test$emails),]

test %>% distinct()

write.csv(test, file="data/greedy_approach.csv")
```
### Check validity
```{r}
coded <- read.csv(file="data/greedy_approach_coded.csv", stringsAsFactors = F)
coded <- coded[!is.na(coded$valid),]

table(coded$valid)

paste0("Precision of greedy approach is ", (table(coded$valid)[1]/sum(table(coded$valid)))*100, "%")
```

## More conservative approach
Check only against first and last name
```{r}
# Match
cmplt = mrg_data#[,c(1:3,57:63)]
cmplt$match = as.numeric(1)
cmplt = as.data.frame(cmplt)
cmplt$emails_p = stri_extract_first_regex(cmplt$emails, "^[^@]+")

# replica mrg_data to see the difference between the two approaches
mrg_replica = mrg_data
for (i in 1:nrow(cmplt)) {
  mrg_replica$match[i] = sum(stri_detect_fixed(
    pattern = c(
      ifelse(is.na(tolower(mrg_replica$last.v1.clean[i])), "jhgaskhdsg", tolower(mrg_replica$last.v1.clean[i])),
      ifelse(is.na(tolower(mrg_replica$first.v1.clean[i])), "jhgaskhdsg", tolower(mrg_replica$first.v1.clean[i]))
    ),
    str = cmplt$emails_p[i]
  ))
}

test_conservative= mrg_replica[mrg_replica$match!=0,]
test_conservative= as.data.frame(test_conservative)
test_conservative =test_conservative[!is.na(test_conservative$emails),]

test_conservative %>% distinct()

write.csv(test_conservative, file="data/conservative_approach.csv")

# Not bad, from a first quick check: almost all valid
```
### Check validity
```{r}
coded_conservative <- read.csv(file="data/conservative_approach_coded.csv", stringsAsFactors = F)
coded_conservative <- coded_conservative[!is.na(coded_conservative$valid),]

table(coded_conservative$valid)

paste0("Precision of conservative approach is ", (table(coded_conservative$valid)[1]/sum(table(coded_conservative$valid)))*100, "%")
```

# Full dataset 
I am using the conservative approach since it will drastically reduce manual coding labour whilst still yielding a large number of valid email addresses.

## Including the names of EU and legal individuals 
```{r}
# Match
cmplt = mrg_data#[,c(1:3,57:63)]
cmplt$match = as.numeric(1)
cmplt = as.data.frame(cmplt)
cmplt$emails_p = stri_extract_first_regex(cmplt$emails, "^[^@]+")

# replica mrg_data to see the difference between the two approaches
mrg_final = mrg_data


# Create name search fields for both EU as well as legal staff
##match names and emails of PER organization
mrg_final$last.EU = str_extract(mrg_final$Person.in.charge.of.EU.relations, '[^ ]+$')
mrg_final$first.EU = word(mrg_final$Person.in.charge.of.EU.relations, 1)
mrg_final$last.legal = str_extract(mrg_final$Person.with.legal.responsibility, '[^ ]+$')
mrg_final$first.legal = word(mrg_final$Person.with.legal.responsibility, 1)
# Other name combinations (courtesy of Saar Alon-Barkat's Github)
## first EU people
t1 <- str_split(mrg_final$last.EU,"-", simplify = TRUE) %>% 
  data.frame() %>% 
  mutate(last.EU.v1 = X1 %>% as.character(),
         last.EU.v2 = X2 %>% as.character()) %>%
  select(-X1,
         -X2) %>% 
  mutate(last.EU.v2 = na_if(last.EU.v2,""))
mrg_final$last.EU.v1 = t1$last.EU.v1
mrg_final$last.EU.v2 = t1$last.EU.v2

t1_first.EU <- str_split(mrg_final$first.EU,"-", simplify = TRUE) %>% 
  data.frame() %>% 
  mutate(first.EU.v1 = X1 %>% as.character(),
         first.EU.v2 = X2 %>% as.character()) %>%
  select(-X1,
         -X2) %>% 
  mutate(first.EU.v2 = na_if(first.EU.v2,""))
mrg_final$first.EU.v1 = t1_first.EU$first.EU.v1
mrg_final$first.EU.v2 = t1_first.EU$first.EU.v2

mrg_final <- mrg_final %>% 
  #cleaning first.EU and last.EU names
  mutate(first.EU.v1.clean = first.EU.v1 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""),
         first.EU.v2.clean = first.EU.v2 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""),
         last.EU.v1.clean = last.EU.v1 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""),
         last.EU.v2.clean = last.EU.v2 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""))

## now legal people
t1 <- str_split(mrg_final$last.legal,"-", simplify = TRUE) %>% 
  data.frame() %>% 
  mutate(last.legal.v1 = X1 %>% as.character(),
         last.legal.v2 = X2 %>% as.character()) %>%
  select(-X1,
         -X2) %>% 
  mutate(last.legal.v2 = na_if(last.legal.v2,""))
mrg_final$last.legal.v1 = t1$last.legal.v1
mrg_final$last.legal.v2 = t1$last.legal.v2

t1_first.legal <- str_split(mrg_final$first.legal,"-", simplify = TRUE) %>% 
  data.frame() %>% 
  mutate(first.legal.v1 = X1 %>% as.character(),
         first.legal.v2 = X2 %>% as.character()) %>%
  select(-X1,
         -X2) %>% 
  mutate(first.legal.v2 = na_if(first.legal.v2,""))
mrg_final$first.legal.v1 = t1_first.legal$first.legal.v1
mrg_final$first.legal.v2 = t1_first.legal$first.legal.v2

mrg_final <- mrg_final %>% 
  #cleaning first.legal and last.legal names
  mutate(first.legal.v1.clean = first.legal.v1 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""),
         first.legal.v2.clean = first.legal.v2 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""),
         last.legal.v1.clean = last.legal.v1 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""),
         last.legal.v2.clean = last.legal.v2 %>% replace_non_ascii() %>% str_to_lower() %>% str_replace_all("\\W",""))

# Do matching for both legal as well as EU staff
for (i in 1:nrow(cmplt)) {
  mrg_final$match[i] = sum(stri_detect_fixed(
    pattern = c(
      ifelse(is.na(tolower(mrg_final$last.EU.v1.clean[i])), "jhgaskhdsg", tolower(mrg_final$last.EU.v1.clean[i])),
      ifelse(is.na(tolower(mrg_final$first.EU.v1.clean[i])), "jhgaskhdsg", tolower(mrg_final$first.EU.v1.clean[i])),
      ifelse(is.na(tolower(mrg_final$last.legal.v1.clean[i])), "jhgaskhdsg", tolower(mrg_final$last.legal.v1.clean[i])),
      ifelse(is.na(tolower(mrg_final$first.legal.v1.clean[i])), "jhgaskhdsg", tolower(mrg_final$first.legal.v1.clean[i]))
    ),
    str = cmplt$emails_p[i]
  ))
}

# Indicate if the person is a legal staffer with $match_legal
for (i in 1:nrow(cmplt)) {
  mrg_final$match.legal[i] = sum(stri_detect_fixed(
    pattern = c(
      ifelse(is.na(tolower(mrg_final$last.legal.v1.clean[i])), "jhgaskhdsg", tolower(mrg_final$last.legal.v1.clean[i])),
      ifelse(is.na(tolower(mrg_final$first.legal.v1.clean[i])), "jhgaskhdsg", tolower(mrg_final$first.legal.v1.clean[i]))
    ),
    str = cmplt$emails_p[i]
  ))
}

#Create dataset with all matches
test_final= mrg_final[mrg_final$match!=0,]
test_final= as.data.frame(test_final)
test_final =test_final[!is.na(test_final$emails),]

#remove or correct faulty emails
test_final$emails = str_remove(test_final$emails, "\\.$") # remove emails that end on a dot
test_final$emails = str_remove(test_final$emails, ".+?\\.png$") # remove image addresses
test_final =test_final[!is.na(test_final$emails),]
test_final =test_final[test_final$emails!="",]

#remove duplicates
test_final = test_final %>% distinct()


#save dataset
write.csv(test_final, file="data/transparency_emails_final.csv")
```
# Check representativeness of email sample
```{r}
rprs = test_final%>% distinct(website, .keep_all = T)
# Original
prpt = trns %>% 
  group_by(Section) %>% 
  summarise(n=n()) %>% 
  mutate(freq = n/sum(n)) 
# Sample
prpt_smpl = rprs %>% 
  group_by(Section) %>% 
  summarise(n=n()) %>% 
  mutate(freq = n/sum(n))
```

